Make any stupid plot you want

### 2020-12-03 draft/sections/math.tex
spivak! up to schemas

\begin{itemize}
\item $A$ is the function that converts an instance of data $\Gamma(E)$ to an instance of a visual representation $\Gamma(H)$ 
\item $E$ is a locally trivial fiber bundle over $K$ representing data space.
\item $K$ is a triangulizable space encoding the connectivity of the observations in the data. 
\item $H$ is a fiber bundle over $S$ representing visual space
\item $S$ is a simplacial complex of triangles encoding the connectivity of the visualization of $\Gamma(E)$
\end{itemize}

@@

where there is a bijection from $F$ to every fiber $F_k$ over point $k \in K$ in $E$ and the function $\pi: E \rightarrow K$ is the map into the $K$ quotient space of $E$.

Every point in the base space $k \in K$ has a local neighborhood $U$ \cite{FiberBundle2020, rowlandFiberBundle}

\begin{equation}
    \begin{tikzcd}
        \pi^{-1}(U) \arrow[r, "\varphi" description] \arrow[d, "\pi" description] & U \times F \arrow[ld, "\mathrm{proj}_U"] \\
        U                                                                         &                                         
    \end{tikzcd}
\end{equation}
$\varphi: \pi^{-1}(U) \rightarrow U \times F$ is a homeomorphism such that $\pi$ and $\mathrm{proj}_U$ both map to $U$, the fiber over $k$ $F_k = \pi^{-1}({k \in K}) $ is homomorphic to the fiber $F$.  The base space $K$ carries the quotient topology determined by $\pi$, meaning it is

meaning that for every point $k in K$ there exists an open set neighborhood $U$ such that if $E$ is restricted to $k$ , then  $\iota*E = F\times U$. 
\begin{equation}
abc
\end{equation}

The function $\pi$ is the mapping from a point on a specific fiber $F_{k}|k\in K$ in $E$ to a location $k \in K$. The section $\sigma$ is the mapping from locations $k$ on $K$ to points on $F_{k}$ in $E$
\begin{equation}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi" description, bend right ] \\
                        & K \arrow[u, "\sigma", description, bend right]
    \end{tikzcd}
\end{equation}

such that it is the right inverse of $\pi$:
\begin{equation}
    \pi(\sigma(k)) = k \text{ for all } k \in K 
\end{equation}

@@

where the fiber at $k$, $F_k$,  is the domain of $g(k)$.  The space of global sections $\sigma$ of $E$ is $\Gamma(E)$:

\begin{figure}[ht]
    \label{fig:fiberbundle}
    \includegraphics[width=.2\linewidth]{figures/sections/math/fiberbundle.png}
    \caption{write up some words here}
    %% simpler still replace w/ timeseries of temp, 1D fiber -> inspired by butler 1989 FIgG 1
\end{figure}

@@

\subsubsection{Base Space $K$}

K is a triangulizable topological space.

\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_1k.png}
\end{figure}
\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_2k.png}
\end{figure}
%% general statement about topology, examples of 0, 1, ....Ks [none triangular things, square/torus, ....], condition on K is that it can be represent as a triangulation of K (can be realized as triangle on K - extra structure that may be arbitrary
%% k is a topological space ....equation soup

\subsubsection{Fiber Space $F$}
The fiver ver is the set of elements $e \in F$ that lies over 
$F_{k}$ is a fiber over $K$ that lo

Spivak provides a formalization for the values $x \in X$ whereby they can have specialized types. He defines the space of datatypes $\mathrm{DT}$

DT = set of strings names of types
U = set of single elements of type in DT
pi (U-DT)
Also need to take column names (U cross C)

%% C is more about naming types to reuse primatives

@@

\subsubsection{Subset}
$\Gamma(E)$ is the space of all points in $F$ returned by $\sigma$; therefore the points being visualized in a streaming or animation example can be considered a subset that lives on base space $U$ embedded in $K$ with the same fiber $\iota^*E$ and $\iota^*\sigma$.   
\begin{equation}
    \begin{tikzcd}
        \iota^\ast E \arrow[r, hook] \arrow[d]                                                                       & E \arrow[d, bend right]                       \\
        U \arrow[r, "\iota" description, hook] \arrow[u, "\iota^\ast \sigma" description, bend right, shift right=2] & K \arrow[u, "\sigma" description, bend right]
    \end{tikzcd}    
\end{equation}

>>>>

\begin{itemize}
\item $A$ is the function that converts an instance of data $\Gamma(E)$ to an instance of a visual representation $\Gamma(H)$ 
\item $E$ is a locally trivial fiber bundle over $K$ representing data space.
\item $K$ is a triangulizable space encoding the connectivity of the observations in the data. 
\item $H$ is a fiber bundle over $S$ representing visual space
\item $S$ is a simplacial complex of triangles encoding the connectivity of the visualization of $\Gamma(E)$
\item $\sigma: K\rightarrow E$ is the data being visualized
\item $\rho: S \rightarrow H$ is the render map
\end{itemize}

@@

where there is a bijection from $F$ to every fiber $F_k$ over point $k \in K$ in $E$ and the function $\pi: E \rightarrow K$ is the map into the $K$ quotient space of $E$. Every point in the base space $k \in K$ has a local open set neighborhood $U$ \cite{FiberBundle2020, rowlandFiberBundle}

\begin{equation}
    \begin{tikzcd}
        \pi^{-1}(U) \arrow[r, "\varphi" description] \arrow[d, "\pi" description] & U \times F \arrow[ld, "\mathrm{proj}_U"] \\
        U                                                                         &                                         
    \end{tikzcd}
\end{equation}
such that $\varphi: \pi^{-1}(U) \rightarrow U \times F$ is a homeomorphism where $\pi$ and $\mathrm{proj}_U$ both map to $U$ and the fiber over $k$ $F_k = \pi^{-1}({k \in K}) $ is homomorphic to the fiber $F$.

The section $\sigma$ is the mapping $\sigma: K\rightarrow E$ 
\begin{equation}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi" description, bend right]    \\
                          & K \arrow[u, "\sigma" description, bend right]
        \end{tikzcd}
\end{equation}

such that it is the right inverse of $\pi$
\begin{equation}
    \pi(\sigma(k)) = k \text{ for all } k \in K 
\end{equation}

@@

where the domain of $g(k)$ is $F_k$.  The space of sections over $U \subset K$ is called a sheaf and the space of all possible sections $\sigma$ of $E$ is $\Gamma(E)$. All datasets $\sigma \in \Gamma(E)$ have the same variables $F$ and connectivity $K$ but can have different values such that $\sigma_{i}\neq\sigma_{j}$.

\begin{figure}[ht]
    \label{fig:fiberbundle}
    \includegraphics[width=.2\linewidth]{figures/sections/math/fiberbundle.png}
    \caption{write up some words here}
\end{figure}

@@

\subsubsection{Base Space $K$}
K is a triangulizable quotient topological space.
%%insert stuff about qotient spaces....

\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_1k.png}
\end{figure}
\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_2k.png}
\end{figure}

\subsubsection{Fiber Space $F$}
Spivak models the fiber space $F$ as schema and the data as sheafs (localized $\sigma$ functions) on the schema \cite{spivakSIMPLICIALDATABASES}. He defines the type specification 
\begin{equation}
\pi: U \rightarrow DT
\end{equation}

where $DT$ is the set of data types (as identified by their names) and $U$ is the set of all possible objects $x$ of all types in $DT$. This means that for each type $T\in DT$, the preimage $\pi^{1}(T)\subset U $ is the domain of $T$, and a value $x \in \pi^{1}(T)\subset U$ is an object of type $T$. Spivak then defines a schema $(C, \sigma)$ of type $\pi$, where $\pi$ is the universe of all types, such that 
\begin{equation}
\sigma: C \rightarrow DT
\end{equation}
where $C$ is a finite ordered set of columns in a database. We extend C to refer to the names of all distinct

@@

\subsubsection{Subset}
$\Gamma(E)$ is the space of all points in $F$ returned by $\sigma$; therefore the points being visualized in a streaming or animation example can be considered a subset that lives on base space $U \subset K$ with the same fiber $F$
\begin{equation}
    \begin{tikzcd}
        \iota^\ast E \arrow[r, hook] \arrow[d]                                                                       & E \arrow[d, bend right]                       \\
        U \arrow[r, "\iota" description, hook] \arrow[u, "\iota^\ast \sigma" description, bend right, shift right=2] & K \arrow[u, "\sigma" description, bend right]
    \end{tikzcd}    
\end{equation}
where $\iota^*E$ and $\iota^*\sigma$ are $E$ and $\sigma$ restricted to points $k \in U \subset K$.
